---
title: 'The Book of R: Chap 02'
output:
  html_document:
    df_print: paged
---

# Chapter 02: Numerics, Arithmetic, Assignment and Vectors

## Exercise 2.4
  
  <ol type="a">
    <li>Create and store a vector that contains the following, in this order:</li>
      <ul>
        <li>A sequence of length 5 from 3 to 6 (inclusive)</li>
        <li>A twofold repetition of the vector $c(2, -5.1, -33)$</li>
        <li>The value $\dfrac{7}{42} + 2$</li>
      </ul>
```{r}
vec.1 <- seq(from=3, to=6, length.out=5)
vec.1
vec.2 <- rep(c(2, -5.1, -33), each=2)
vec.2
vec.3 <- c(7/42 + 3)
vec.3
vec.a <- c(vec.1, vec.2, vec.3)
vec.a
```
    <li>Extract the first and the last elements of your vector from (a), storing then as a new object.</li>
```{r}
vec.b <- vec.a[c(1,length(vec.a))]
vec.b
```
    <li>Store as a third object the values returned by omitting the first and the ast of your vector from (a).</li>
```{r}
vec.c <- vec.a[-c(1,length(vec.a))]
vec.c
```
    <li>Use only (b) and (c) to reconstruct (a).</li>
```{r}
vec.d <- c(vec.b[1], vec.c, vec.b[2])
vec.d
```
    <li>Overwrite (a) with the same values sorted from smallest to largest.</li>
```{r}
vec.a <- sort(vec.a, decreasing = FALSE)
vec.a
```
    <li>Use the colon operator as an index vector to reverse the order of (e), and confirm this is identical to using sort on (e) with decreasing=TRUE</li>
```{r}
vec.f <- vec.a[c(length(vec.a):1)]
vec.f
all(vec.f == sort(vec.a, decreasing = TRUE))
```
    <li>Create a vector from (c) that repeats the third element of (c) thee times, the six element four times and the last element once.</li>
```{r}
c(rep(vec.c[3], 3), rep(vec.c[6], 4), vec.c[length(vec.c)])
```
    <li>Create a new vector as copy of (e) by assigning (e) as is to a newly named object. Using this new copy of (e), overwrite the first, the fifth to the seventh (inclusive), and the last element with the values 99 to 95 (inclusive), repectively.</li>
```{r}
vec.e.copy <- vec.a
values_to_replace <-seq(from=99, to=95)
vec.e.copy[1] <- values_to_replace[1]
vec.e.copy[5:7] <- values_to_replace[2:4]
vec.e.copy[length(vec.e.copy)] <- values_to_replace[length(values_to_replace)]
vec.e.copy
```
  </ol>
  